### 2019-07-09 monograph/thesis/chapters/beautifiers.tex
Moved invalid sections from beautifiers.tex to
monograph/thesis/chapters/object_beautifier.tex

\lang{%
    On \citeonline{programIndentation} was analyzed the level of program comprehension which can be gained by the indentation and
    was comprehended that the indentation levels of 2 and
    4 spaces proved to have the best comprehension levels again other levels.
}{%
    Em \citeonline{programIndentation} foi analisado o nível de compreensão do programa que pode ser obtido pela indentação e
    foi constatado que os níveis de indentação de 2 e
    4 espaços provaram ter os melhores níveis de compreensão do que outros níveis.
}%
\begin{citacao}
    % \setlength{\itemindent}{5pt}
    Por mais absurdo que possa parecer,
    lutar sobre espaços em branco e
    outras questões aparentemente triviais de layout de código~=fonte é realmente justificado.
    Desde que feito com moderação,
    abertamente,
    de uma forma justa e
    com construção de consenso,
    sem esfaquear os seus companheiros de equipe ao longo do caminho.
    \cite[tradução nossa]{deathToTheSpaceInfidels}\footnote{
    \englishword{%
    So yes,
    absurd as it may sound,
    fighting over whitespace characters and
    other seemingly trivial issues of code layout is actually justified.
    Within reason of course -- when done openly,
    in a fair and
    concensus building way,
    and without stabbing your teammates in the face along the way.
    }}.
\end{citacao}

@@

TODO.

@@

\subsection{Configuration Detection}

If found on the project root folder,
a folder named `.object~=beauty',
it will be used to store the automatically generated configurations based on the current configuration\s rules.
Such thing,
cannot be easily implemented because of the various complexities which can be introduced into the formatting rules.
For example,
the if configurations rules are simple and
limited to just changing simple aspects of the formatting,
then the configuration generation will also be simple,
because there are only a few aspects to analyze.
However,
as the formatting rules grow up,
their complexity equally proportionally grows,
due the increased count of possibilities to analyze when combined together.

\subsection{Multidirectional Translation}

With this ObjectBeautifier,
we can edit XML files like YAML files,
because the when we load the XML,
we create a copy (the YAML version of the XML) on the `.object~=beauty` folder which is edited by Sublime Text,
and let the XML on its original place.
Then when we save our YAML copy,
we translate it to the XML original copy.
Similarly,
for a C language code,
it would be like to change some bit on the compiled binary code and
have the change reflected on the original C source code.
\url{https://github.com/Microsoft/XmlNotepad}

Open Source Neural Machine Translation in Torch,
translates between languages by machine learning.
\url{https://github.com/OpenNMT/OpenNMT}

@@

TODO

>>>>

\lang{%
    On \citeonline{programIndentation} was analyzed the level of program comprehension which can be gained by the indentation and
    was comprehended that the indentation levels of 2 and
    4 spaces proved to have the best comprehension levels again other levels.
}{%
    Em \citeonline{programIndentation} foi analisado o nível de compreensão do programa que pode ser obtido pela indentação e
    foi constatado que os níveis de indentação de 2 e
    4 espaços provaram ter os melhores níveis de compreensão do que outros níveis.
}%
\begin{citacao}
    % \setlength{\itemindent}{5pt}
    Por mais absurdo que possa parecer,
    lutar sobre espaços em branco e
    outras questões aparentemente triviais de layout de código~=fonte é realmente justificado.
    Desde que feito com moderação,
    abertamente,
    de uma forma justa e
    com construção de consenso,
    sem esfaquear companheiros de equipe ao longo do caminho.
    \cite[tradução nossa]{deathToTheSpaceInfidels}\footnote{
    \englishword{%
    So yes,
    absurd as it may sound,
    fighting over whitespace characters and
    other seemingly trivial issues of code layout is actually justified.
    Within reason of course -- when done openly,
    in a fair and
    concensus building way,
    and without stabbing your teammates in the face along the way.
    }}.
\end{citacao}

@@

@@

@@

### 2019-07-09 monograph/thesis/chapters/object_beautifier.tex
Removed redundant \phantomsection text messages from all chapters
Translated the first page for theorybase.tex
Moved Related Works section from object_beautifier.tex to
monograph/thesis/chapters/beautifiers.tex section.
Moved invalid sections from beautifiers.tex to
monograph/thesis/chapters/object_beautifier.tex

@@

\section{\lang{Related Works}{Trabalhos Relacionados}}

\url{http://editorconfig.org/}

>>>>

\subsection{Configuration Detection}

If found on the project root folder,
a folder named `.object~=beauty',
it will be used to store the automatically generated configurations based on the current configuration\s rules.
Such thing,
cannot be easily implemented because of the various complexities which can be introduced into the formatting rules.
For example,
the if configurations rules are simple and
limited to just changing simple aspects of the formatting,
then the configuration generation will also be simple,
because there are only a few aspects to analyze.
However,
as the formatting rules grow up,
their complexity equally proportionally grows,
due the increased count of possibilities to analyze when combined together.

@@

\subsection{Multidirectional Translation}

With this ObjectBeautifier,
we can edit XML files like YAML files,
because the when we load the XML,
we create a copy (the YAML version of the XML) on the `.object~=beauty` folder which is edited by Sublime Text,
and let the XML on its original place.
Then when we save our YAML copy,
we translate it to the XML original copy.
Similarly,
for a C language code,
it would be like to change some bit on the compiled binary code and
have the change reflected on the original C source code.
\url{https://github.com/Microsoft/XmlNotepad}

Open Source Neural Machine Translation in Torch,
translates between languages by machine learning.
\url{https://github.com/OpenNMT/OpenNMT}
